### 2021-07-02 doc/thesis/chapters/dsp.tex
receiver types (see literature)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Superheterodyne Receiver}

Multiple different receiver structures exist and are implemented in receivers.
A very common structure is the so-called superheterodyne receiver.
In the literature, short forms like \textit{superhet}, or simply \textit{super} are found.

The main characteristic of a superhet is, that it converts the radio-frequency (RF) antenna signal to an IF in a first stage, instead of going to baseband directly.\\

@@

from HF to BB\\
math. formulas

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Receiver types}

Multiple different receiver architectures exist and are implemented in receivers.
Two common examples are explained in the following sections.

\subsection{Direct-Conversion Receiver}

A direct-conversion receiver, as its name suggests, converts an RF signal to baseband directly.
It can also be called homodyne, synchrodyne, or zero-IF receiver.

In order to achieve direct down-conversion, the local oscillator of the mixer needs to be set exactly to the center frequency of the desired signal.

\subsection{Superheterodyne Receiver}

The superheterodyne receiver is often found in the literature with short forms like \textit{superhet}, or simply \textit{super}.
The main characteristic of a superhet is, that it converts the radio-frequency (RF) antenna signal to an IF in a first stage, instead of going to baseband directly.\\

@@

The process of down-conversion is used to convert an RF signal to a signal of lower frequency, while preserving its information content.
This is the explanation in the time domain.
However, it may be easier look at the process in the frequency domain.
In the frequency domain, the band-limited RF signal is shifted down to a lower frequency.
This lower frequency can either be zero, i.e. baseband, or an intermediate frequency, such as in the application of a superheterodyne receiver.

math. formulas\\
digital: meet nyquist criteria, just like any other DSP (show in spectrum)\\
